---
title: "blogdown demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

## Make a blogdown project

Open up RStudio, New project -> Blogdownproject

`blogdown::serve_site()`

## Tour of directory

Check out the following directories

- `content`
- `templates`
- `static`
- `public`
- `themes`

## Install new theme

I've had mixed results on downloading themes featured on gohugo.io. The cost of not really knowing how things work and downloading a fancy theme means that I can't really fix things when they break. 

Example: [Charaka](https://themes.gohugo.io/charaka-hugo-theme/)

```{r}
blogdown::install_theme("natarajmb/charaka-hugo-theme")
```



Here's one that works

I like simple themes, so let's try using [Tailwind Journal](https://github.com/ianrodrigues/hugo-tailwind-journal)

```{r}
blogdown::install_theme("ianrodrigues/hugo-tailwind-journal")
```

Also another that works, [Solar](https://themes.gohugo.io/solar-theme-hugo/)
```{r}
blogdown::install_theme("bake/solar-theme-hugo")
```


## Ship to netlify

Netlify works on building your dir from a github repo, so we'll need to put the dir under version control, and we can ignore `public/`, as that will be rebuilt on Netlify

Push to a github repo

log into Netlify

In setting up github, give it access to all your current and future repos

deploy, and we're good!


